\subsection{The {\tt CLM:} module}\label{sect:CLMData}

The {\tt CLM:} module is called to mix and redistribute several liquid mixtures containing identical isotopes contents (different isotopic densities). The module can also change the density of any isotope in the mixture. The calling specifications are:

\begin{DataStructure}{Structure \dstr{CLM:}}
\dusa{MICLIB} \moc{:=} \moc{CLM:} \dusa{MICLIB}   \moc{::} \dstr{descclm}
\end{DataStructure}

\noindent
where

\begin{ListeDeDescription}{mmmmmmmm}

\item[\dusa{MICLIB}] {\tt character*12} name of the \dds{microlib} that will
contain the microscopic and macroscopic cross sections updated by the
module. 

\item[\dstr{descclm}] structure describing the clm options.

\end{ListeDeDescription}

\
\subsubsection{Data input for module {\tt CLM:}}\label{sect:descclm}

\begin{DataStructure}{Structure \dstr{descclm}}
$[$ \moc{EDIT} \dusa{iprint} $]$ \\
\moc{MIXCLM} (idclm(ii),ii=1,nclm) \\
$[$ $\{$ \moc{ADDI} $|$ \moc{SETI} $\}$ $\{$ \moc{ABS} $|$ \moc{REL} $\}$ (isot(ii) dens(ii),ii=1,niso) $]$ \\
{\tt ;}
\end{DataStructure}
\noindent
where

\begin{ListeDeDescription}{mmmmmmmm}

\item[\moc{EDIT}] keyword used to modify the print level \dusa{iprint}.

\item[\dusa{iprint}] index used to control the printing of this module. The
amount of output produced by this module will vary substantially
depending on the print level specified. 

\item[\moc{MIXCLM}] keyword to specify that several liquid mixtures will be combined to replace the original mixtures. This combination will take into account the volume occupied by each mixture.

\item[\moc{idclm}] mixture number to combine.

\item[\moc{ADDI}] to add a isotope concentration to that of this  isotope in the combined mixture, 
\item[\moc{SETI}] to set the concentration of an isotope in the combined mixture to a fix value.

\item[\moc{ABS}] isotopic concentration in $10^{24}$ cm$^{-3}$.

\item[\moc{REL}] relative concentration with respect with the concentration of an isotope in the combined mixture.

\item[\moc{isot}] reference name of isotope to process.

\item[\moc{dens}] absolute or relative density for this isotope.


\end{ListeDeDescription}
\eject
